Conflict Analysis for Mixed-integer SDPs

### 2022-06-16 tex/ConflictAnalysis.tex
one more reference
extend description at bit

@@

Moreover, one can take an objective cutoff into account. Namely, assume
that $y^\star$ is a feasible solution to~\eqref{MISDP}. We are then only
interested in solutions that are at least as good, i.e.,
$b\T y \leq b\T y^\star$ or $- b\T y \geq - b\T y^\star$. Adding this
inequality to~\eqref{eq:ConflictCut} yields:
\begin{align*}
  & \sum_{j=1}^m \skal{A^j}{\hat{X}} y_j + \hat{z}\T D y - b\T y \geq
    \skal{A^0}{\hat{X}} + \hat{z}\T d - b\T y^\star\\
  \Leftrightarrow\quad
  & \sum_{j=1}^m \big(\skal{A^j}{\hat{X}} + (\hat{z}\T D)_j - b_j\big) y_j \geq
    \skal{A^0}{\hat{X}} + \hat{z}\T d - b\T y^\star.
\end{align*}

>>>>

Very similar ideas are needed for an outer approximation algorithm, in
which one adds aggregated inequalities that will cut off nodes that are
infeasible or bound exceeding. Coey et al.~\cite{CoeLV20} describe such an
algorithm for mixed-integer conic problems (including MISDP).

@@

Moreover, one can take an objective cutoff into account. Namely, assume
that $y^\star$ is a feasible solution to~\eqref{MISDP}. We are then only
interested in solutions that are at least as good, i.e.,
$b\T y \leq b\T y^\star$ or $- b\T y \geq - \overline{b}$, where
$\overline{b} = b\T y^\star - \varepsilon$ for $\varepsilon > 0$. Adding
this inequality to~\eqref{eq:ConflictCut} yields:
\begin{align*}
  & \sum_{j=1}^m \skal{A^j}{\hat{X}} y_j + \hat{z}\T D y - b\T y \geq
    \skal{A^0}{\hat{X}} + \hat{z}\T d - \overline{b}\\
  \Leftrightarrow\quad
  & \sum_{j=1}^m \big(\skal{A^j}{\hat{X}} + (\hat{z}\T D)_j - b_j\big) y_j \geq
    \skal{A^0}{\hat{X}} + \hat{z}\T d - \overline{b}.
\end{align*}

If the mixed-integer feasible point $y^\star$ was produced by the current
node relaxation, then this cut will cut off~$y^\star$: First, by
complementary slackness, the aggregated inequalities are satisfied with
equality. Moreover, $b\T y \leq \overline{b} < b\T y^\star$ will be
violated by construction. Thus, $y^\star$ is cut off. It remains to see
whether propagation of the local bounds at this node will detect
infeasibility.
